\section{So you have a bare board, now what?}

Ok, you have the bare PCB, and it's going to need components installed on it to function as a EMS. This is what you need to do:

These first couple steps are in no particular order.

1. Get the BOM from site, its in csv format, so you can select what modules you want populated.
A few things to note:
EGT circuit won't work, it has a 500°C limit.
The usb connector is plain wrong. In the BOM you can choose to buy a cable to use this wrong (female-A) connector, or buy another usb connector and hack things to install it.
You don't want the shutdown circuit, so its FETs aren't in the BOM. Don't worry about that.

Once you are decided about the BOM, go to to digikey and place the order.

2. modify the board as shown in “Spin 1 specific notes”

We recommend doing these steps sequentially.

1. Install MCU and critical components.
2. Test the MCU works by uploading the firmware
3. install rpm input circuit choose hall input, or VR
4. install misc outputs like Fuel, ect
5. install injectors circuits
6. install ignitions circuits

You now have a PUMA board with components, now what?

You will likely want to verify the board is good with a Jim Stim  then it will need the initial firmware installed. If PUMA was purchased assembled, these steps should not be required, and you can proceed to the next step.

	Testing your board with Jim Stim.

Blah blah blah, fill in this stuff.

	Uploading the initial firmware.

BDM loader notes and more blah blah blah. 
 